Representation Learning for Generalized Planning - SAT Encodings

### 2020-09-03 doc/encodings/paper.tex
Experiments adjustments

% our packages
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{bm}
\usepackage{booktabs}
%\usepackage[inline]{enumitem}
%\usepackage{mathtools}
%\usepackage{multirow}
%\usepackage[mode=buildnew,subpreambles=true]{standalone}
\usepackage{subcaption}
%\usepackage{todonotes}
\usepackage[table]{xcolor}  % TODO Comment out for final submission
%\usepackage{pgfplots}
%\usepackage{tikz}
\usepackage{natbib}

@@

\begin{verbatim}
0. n(a) DECs AND n-ontable NILs AND n-ontable>0
1. n(a) NILs AND n-ontable INCs AND n-ontable>0
\end{verbatim}

\subsection{Blocks:on}
\begin{verbatim}
0. clear(a) ADDs AND holding(·) ADDs AND n-single-blocks INCs AND not-clear(b) NILs
1. clear(a) DELs AND holding(·) ADDs AND n-single-blocks DECs AND not-clear(b) NILs AND not-clear(b)=0
2. clear(a) NILs AND clear(a)=0 AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs
3. clear(a) ADDs AND holding(·) DELs AND n-single-blocks NILs AND not-clear(b) ADDs
4. clear(a) ADDs AND holding(·) DELs AND n-single-blocks INCs AND not-clear(b) NILs AND not-clear(b)>0
5. clear(a) NILs AND clear(a)>0 AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs AND not-clear(b)>0
6. clear(a) DELs AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs
7. clear(a) NILs AND clear(a)=0 AND holding(·) DELs AND n-single-blocks INCs AND not-clear(b) NILs AND not-clear(b)>0
8. clear(a) NILs AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks=0 AND not-clear(b) NILs AND not-clear(b)=0
9. clear(a) NILs AND clear(a)=0 AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) NILs
10. clear(a) ADDs AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) NILs AND not-clear(b)>0
11. clear(a) NILs AND clear(a)>0 AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks>0 AND not-clear(b) NILs
12. clear(a) ADDs AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) ADDs
13. clear(a) DELs AND holding(·) ADDs AND n-single-blocks INCs AND not-clear(b) NILs AND not-clear(b)=0
14. clear(a) NILs AND clear(a)=0 AND holding(·) ADDs AND n-single-blocks INCs AND not-clear(b) DELs
15. clear(a) NILs AND clear(a)=0 AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks>0 AND not-clear(b) NILs AND not-clear(b)=0
16. clear(a) NILs AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) DELs
17. clear(a) NILs AND clear(a)>0 AND holding(·) ADDs AND n-single-blocks INCs AND n-single-blocks>0 AND not-clear(b) DELs
18. clear(a) ADDs AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs
19. clear(a) NILs AND clear(a)>0 AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks=0 AND not-clear(b) NILs AND not-clear(b)>0
20. clear(a) NILs AND clear(a)>0 AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) NILs AND not-clear(b)>0
\end{verbatim}

>>>>

% our packages
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{bm}
\usepackage{booktabs}
%\usepackage[inline]{enumitem}
%\usepackage{mathtools}
%\usepackage{multirow}
%\usepackage[mode=buildnew,subpreambles=true]{standalone}
\usepackage{subcaption}
%\usepackage{todonotes}
\usepackage[table]{xcolor}  % TODO Comment out for final submission
%\usepackage{pgfplots}
%\usepackage{tikz}
\usepackage{natbib}
\usepackage{fancyvrb}

@@

\begin{Verbatim}[fontsize=\footnotesize]
0. n(a) DECs AND n-ontable NILs AND n-ontable>0
1. n(a) NILs AND n-ontable INCs AND n-ontable>0
\end{Verbatim}

\subsection{Blocks:on}
\begin{Verbatim}[fontsize=\footnotesize]
0. clear(a) ADDs AND holding(·) ADDs AND n-single-blocks INCs AND not-clear(b) NILs
1. clear(a) DELs AND holding(·) ADDs AND n-single-blocks DECs AND not-clear(b) NILs AND not-clear(b)=0
2. clear(a) NILs AND clear(a)=0 AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs
3. clear(a) ADDs AND holding(·) DELs AND n-single-blocks NILs AND not-clear(b) ADDs
4. clear(a) ADDs AND holding(·) DELs AND n-single-blocks INCs AND not-clear(b) NILs AND not-clear(b)>0
5. clear(a) NILs AND clear(a)>0 AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs AND not-clear(b)>0
6. clear(a) DELs AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs
7. clear(a) NILs AND clear(a)=0 AND holding(·) DELs AND n-single-blocks INCs AND not-clear(b) NILs AND not-clear(b)>0
8. clear(a) NILs AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks=0 AND not-clear(b) NILs AND not-clear(b)=0
9. clear(a) NILs AND clear(a)=0 AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) NILs
10. clear(a) ADDs AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) NILs AND not-clear(b)>0
11. clear(a) NILs AND clear(a)>0 AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks>0 AND not-clear(b) NILs
12. clear(a) ADDs AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) ADDs
13. clear(a) DELs AND holding(·) ADDs AND n-single-blocks INCs AND not-clear(b) NILs AND not-clear(b)=0
14. clear(a) NILs AND clear(a)=0 AND holding(·) ADDs AND n-single-blocks INCs AND not-clear(b) DELs
15. clear(a) NILs AND clear(a)=0 AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks>0 AND not-clear(b) NILs AND not-clear(b)=0
16. clear(a) NILs AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) DELs
17. clear(a) NILs AND clear(a)>0 AND holding(·) ADDs AND n-single-blocks INCs AND n-single-blocks>0 AND not-clear(b) DELs
18. clear(a) ADDs AND holding(·) ADDs AND n-single-blocks NILs AND not-clear(b) NILs
19. clear(a) NILs AND clear(a)>0 AND holding(·) DELs AND n-single-blocks INCs AND n-single-blocks=0 AND not-clear(b) NILs AND not-clear(b)>0
20. clear(a) NILs AND clear(a)>0 AND holding(·) DELs AND n-single-blocks DECs AND not-clear(b) NILs AND not-clear(b)>0
\end{Verbatim}

\subsection{Gripper}
One simple (smallest) standard instance, 4 blocks, two rooms.
1 iteration
CNF Theory: 34418 vars + 124935 clauses
835 features
Number of transitions/equivalence classes: 1140/65
concept size bound=10,
Optimal MAXSAT solution with cost 5 found

\begin{Verbatim}[fontsize=\footnotesize]
0. ncarried NILs AND ncarried=0 AND robby-at-B DECs
1. ncarried DECs AND robby-at-B NILs AND robby-at-B>0
2. ncarried INCs AND ncarried=0 AND robby-at-B NILs AND robby-at-B=0
3. ncarried NILs AND ncarried>0 AND robby-at-B INCs AND robby-at-B=0
\end{Verbatim}

\subsection{Spanner}
8 instances with different spanner configurations, goal is always the same.
1 iteration
CNF Theory: 466575 vars + 1732026 clauses
724 features
Number of transitions/equivalence classes: 11053/133
concept size bound=8,
Optimal MAXSAT solution with cost 9 found

NOTE: Features of the form $f1>f2$ are not necessary for this solution.

\begin{Verbatim}[fontsize=\footnotesize]
0. bobs-loc-empty NILs AND bobs-loc-empty=0 AND n-items-somewhere DECs AND n-tightened NILs AND n-tightened=0
1. bobs-loc-empty NILs AND bobs-loc-empty>0 AND n-items-somewhere NILs AND n-items-somewhere>0 AND n-tightened NILs AND n-tightened=0
2. bobs-loc-empty DELs AND n-items-somewhere NILs AND n-items-somewhere>0 AND n-tightened NILs AND n-tightened=0
3. bobs-loc-empty NILs AND bobs-loc-empty=0 AND n-items-somewhere NILs AND n-items-somewhere>0 AND n-tightened INCs
4. bobs-loc-empty ADDs AND n-items-somewhere DECs AND n-tightened NILs AND n-tightened=0
\end{Verbatim}

\subsection{Pick Reward}
1 5x5 training instance
3 iteration
CNF Theory: 18519 vars + 76267 clauses
514 features
Number of transitions/equivalence classes: 432/361
concept size bound=8,
Optimal MAXSAT solution with cost 7 found

\begin{Verbatim}[fontsize=\footnotesize]
 1. n-rewards NILs AND n-rewards>0 AND unblocked-dist-to-closest-reward DECs AND unblocked-dist-to-closest-reward>0
 2. n-rewards DECs AND unblocked-dist-to-closest-reward INCs AND unblocked-dist-to-closest-reward=0
\end{Verbatim}
